Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-05-14 paper.tex
Added reference for NWChem.

Another area where the Blue Obelisk has had a signficant impact in the
past five years is in supporting
quantum chemistry calculations and in interpreting their results.
Electronic structure calculations have a long tradition in the
chemistry community and a variety of programs exist, mostly
proprietary software with the notable exception of NWChem.
However, since each program uses different input formats, and the
results are output differently even varying between different versions
of the software, preparing calculations and extracting the results in
an automated way is problematic.

>>>>

Another area where the Blue Obelisk has had a signficant impact in the
past five years is in supporting
quantum chemistry calculations and in interpreting their results.
Electronic structure calculations have a long tradition in the
chemistry community and a variety of programs exist, mostly
proprietary software with the notable exception of NWChem.\cite{NWChem}
However, since each program uses different input formats, and the
results are output differently even varying between different versions
of the software, preparing calculations and extracting the results in
an automated way is problematic.
